Draft

### 2020-09-28 SubGroup.Rmd
no subgroup update

```{r PRAUC CI}
data(P10N10)

s1 <- c(1, 2, 3, 4)
s2 <- c(5, 6, 7, 8)
s3 <- matrix(1:8, 4, 2)

# Join two score vectors
scores1 <- join_scores(s1, s2)

# Join two vectors and a matrix
scores2 <- join_scores(s1, s2, s3)

l1 <- c(1, 0, 1, 1)
l2 <- c(1, 0, 1, 1)
l3 <- c(1, 0, 1, 0)

# Join two label vectors
labels1 <- join_labels(l1, l2)
labels2 <- join_labels(l1, l3)

# A dataset with 20 samples for the good early retrieval performance level
samps3 <- create_sim_samples(20, 10, 10, "good_er")

# Calculate ROC and Precision-Recall curves
sscurves <- evalmod(scores = P10N10$scores, labels = P10N10$labels)

# Specify test dataset IDs names
smmdat1 <- mmdata(scores1, labels2, dsids = c(1,2))

# Use a sample dataset created by the create_sim_samples function
smmdat2 <- mmdata(samps3[["scores"]], samps3[["labels"]], dsids = samps3[["dsids"]])

# Calculate curves for multiple test datasets and keep all the curves
smcurves <- evalmod(smmdat2, raw_curves = TRUE)

autoplot(smcurves, "PRC", show_cb = TRUE)
```

@@

ROCaucTable <- rbind(New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
View(ROCaucTable)
write.csv(ROCaucTable, "Results/ROCaucTable.csv", row.names = F)

## Subgroup Curves
```{r subgroup curves, eval=F}
# subgroup 4 curves

SubgroupPlot <- read.csv("Chapter/Subgroup Table/SubgroupTable.csv")
SubgroupPlot <- SubgroupPlot[, -1]
SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"] <- SubgroupPlot$Score[SubgroupPlot$DeepLearningSystem %in% "CAD4TB"]/100
SubgroupPlot$subgroup <- as.character(SubgroupPlot$subgroup)
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "New"] <- "1.New Case"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Old"] <- "2.Previously Treated Case"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Young"] <- "3.Young age [15,25)"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Middle"] <- "4.Middle age [25,60)"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Senior"] <- "5.Old age [60,108]"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "DOTS"] <- "7.Public DOTS Retesting"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "Referral"] <-"6.Private Public Referral"
SubgroupPlot$subgroup[SubgroupPlot$subgroup %in% "WalkIn"] <-"8.Walk In"
SubgroupPlot$subgroup <- as.factor(SubgroupPlot$subgroup)

SubgroupPlotOrigin <- SubgroupPlot
# SubgroupPlot <- SubgroupPlotOrigin
# Choose the DL System
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "CAD4TB", ]
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "IF2", ]
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "JF1", ]
# SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "Lunit", ]
SubgroupPlot <- SubgroupPlotOrigin[SubgroupPlotOrigin$DeepLearningSystem %in% "qXR", ]

### GO TO AND RUN source("Chapter/Subgroup Table/SubGroupPlot.R")

>>>>

@@

ROCaucTable <- rbind(New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn)
View(ROCaucTable)
write.csv(ROCaucTable, "Results/ROCaucTable.csv", row.names = F)
```
